Comparing Facebook's Prophet Forecasting to an ARIMA Model: A Diebold-Mariano Evaluation of the Top40 Index

### 2017-09-15 template/Draft_Paper.Rmd
Typo edits

# Background 
In this section we will briefly review literature that relates to the comparison of different approaches to forecasting stock returns. This will include both traditional approaches as well new methods such as automatic forecasting, machine learning techniques and quasi-Bayesian forms which incorporate analysts' prior information. The review of literature is concluded a brief introduction to the Diebold-Mariano evaluation and an outline of its suitability for the purpose of this study. The theoretical and mathematical formulation of an ARIMA forecasting model is  then briefly introduced. Thereafter, the theoretical framework and mathematical formulation of Facebooks' Prophet forecasting tool is discussed. Specific attention is drawn to Prophets distinguising features to give the reader an understanding of the value that this forecasting technique can potentially add to stock price prediction. Lastly, the Diebold-Mariano Evaluation technique is introduced as a method of formally testing superior predictive accuracy between two forecasting models.

>>>>

# Background 
In this section we will briefly review literature that relates to the comparison of different approaches to forecasting stock returns. This will include both traditional approaches as well new methods such as automatic forecasting, machine learning techniques and quasi-Bayesian forms which incorporate analysts' prior information. The review of literature is concluded with a brief introduction to the Diebold-Mariano evaluation and an outline of its suitability for the purpose of this study. The theoretical and mathematical formulation of an ARIMA forecasting model is  then briefly introduced. Thereafter, the theoretical framework and mathematical formulation of Facebooks' Prophet forecasting tool is discussed. Specific attention is drawn to Prophets distinguising features to give the reader an understanding of the value that this forecasting technique can potentially add to stock price prediction. Lastly, the Diebold-Mariano Evaluation technique is introduced as a method of formally testing superior predictive accuracy between two forecasting models.

### 2017-09-15 template/Draft_Paper.tex
Typo edits

In this section we will briefly review literature that relates to the
comparison of different approaches to forecasting stock returns. This
will include both traditional approaches as well new methods such as
automatic forecasting, machine learning techniques and quasi-Bayesian
forms which incorporate analysts' prior information. The review of
literature is concluded a brief introduction to the Diebold-Mariano
evaluation and an outline of its suitability for the purpose of this
study. The theoretical and mathematical formulation of an ARIMA
forecasting model is then briefly introduced. Thereafter, the
theoretical framework and mathematical formulation of Facebooks' Prophet
forecasting tool is discussed. Specific attention is drawn to Prophets
distinguising features to give the reader an understanding of the value
that this forecasting technique can potentially add to stock price
prediction. Lastly, the Diebold-Mariano Evaluation technique is
introduced as a method of formally testing superior predictive accuracy
between two forecasting models.

>>>>

In this section we will briefly review literature that relates to the
comparison of different approaches to forecasting stock returns. This
will include both traditional approaches as well new methods such as
automatic forecasting, machine learning techniques and quasi-Bayesian
forms which incorporate analysts' prior information. The review of
literature is concluded with a brief introduction to the Diebold-Mariano
evaluation and an outline of its suitability for the purpose of this
study. The theoretical and mathematical formulation of an ARIMA
forecasting model is then briefly introduced. Thereafter, the
theoretical framework and mathematical formulation of Facebooks' Prophet
forecasting tool is discussed. Specific attention is drawn to Prophets
distinguising features to give the reader an understanding of the value
that this forecasting technique can potentially add to stock price
prediction. Lastly, the Diebold-Mariano Evaluation technique is
introduced as a method of formally testing superior predictive accuracy
between two forecasting models.
